Staged Abstract Interpreters

### 2018-11-16 paper/60_eval.tex
worked on paper
revise intro
Run evaluation

\section{Evaluation}

@@

>>>>

\section{Evaluation} \label{evaluation}

@@

We have designed, implemented and evaluated a prototype abstract interpreter for Scheme.
Our prototype includes both staged and unstaged versions of the abstract interpreter for comparison 
purposes.

We ran our prototype abstract interpreter on a suite of benchmark scheme programs that are also used 
in \cite{Johnson:2013:OAA:2500365.2500604, ashley:practical}.
